Issues with Dynamical Measurements Across the Disk

### 2019-03-18 paper/ms.tex
Small text fixes

For a systematic offset in $z$ ({\em upper} panels), the
95\textsuperscript{th} minus 5\textsuperscript{th} percentiles are $2.2$ and
$6.2 \actunit$ for $J_r$ and $J_z$, respectively. These are fractional errors
of $5.7\%$ and $85.7\%$, respectively. The error induced in $L_z$ is
negligible, as expected since $L_z$ is independent of $z$. It is worth
pointing out that a $100\,\pc$ error in an orbit with
$z_{\text{max}}=850\,\pc$ --- a $12\%$ error
--- induced a $43\%$ error in the computation of $J_z$.

>>>>

For a systematic offset in $z$ ({\em upper} panels), the
95\textsuperscript{th} minus 5\textsuperscript{th} percentiles are $2.2$ and
$6.2\,\actunit$ for $J_r$ and $J_z$, respectively. These are fractional errors
of $5.7\,\%$ and $85.7\,\%$, respectively. The error induced in $L_z$ is
negligible, as expected since $L_z$ is independent of $z$. It is worth
pointing out that a $100\,\pc$ error in an orbit with
$z_{\text{max}}=850\,\pc$ --- a $12\%$ error
--- induced a $43\%$ error in the computation of $J_z$.
